Ontology Matching with word2vec

### 2016-03-16 Paper/Draft.tex
Few comments and typo's

 \section{Introduction}
 % Voorbeeld van semantisch web?
 It is a Friday afternoon and you realise you want to watch a movie with some friends. So, what do you do? To achieve this goal you must take 4 steps.

@@

 \subsection{Overview}
 This thesis is structured as follows.

@@

>>>>

 \section{Introduction}
 It is a Friday afternoon and you realise you want to watch a movie with some friends. So, what do you do? To achieve this goal you must take 4 steps.

@@

 \subsection{Overview}
 This thesis is structured as follows...

@@

 %https://www.researchgate.net/profile/Hai_Dong/publication/260329617_Semantic_Web_Service_matchmakers_State_of_the_art_and_challenges/links/0a85e531190b602215000000.pdf
